\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-22 evaluation.tex
some updates

For the vNext case study, the random scheduler was able to reproduce the bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in \S\ref{sec:psharp:testing} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

For the MigratingTable case study, we evaluated the \psharp test harness of \S\ref{sec:cases:migration} on 11 ``bugs'', including 8 \emph{organic} bugs that actually occurred in development and 3 \emph{notional} bugs (marked $*$), which are other code changes that we deemed interesting ways of making the code incorrect. The test found seven of the organic bugs, which are listed first in Table~\ref{tab:testing}. The remaining four bugs (denoted with $\diamond$) were not caught with our default test harness in the 100,000 iterations (a process that required less than 30 minutes). We believe this is because the inputs and schedules that trigger them are too rare in our distribution. To confirm this, we wrote a custom test case for each bug with a specific input that triggers it and were able to quickly reproduce the bugs, as shown. This method is useful for regression testing, but one could not use it during development with no prior knowledge about the bugs.

>>>>

For the vNext case study, the random scheduler was able to reproduce the ExtentNodeLivenessViolation bug in less than 10 seconds. The reason that the number of scheduling steps to find the bug is much higher than the rest of the bugs in the table is that this bug is a liveness violation: as discussed in \S\ref{sec:psharp:testing} we leave the program to run for a long time before checking if the liveness property holds. The PCT scheduler was unable to find the bug using the bug depth of 2, which suggests that the bug requires a larger depth bound to be found.

For the MigratingTable case study, we evaluated the \psharp test harness of \S\ref{sec:cases:migration} on eleven buggy versions of the system, including eight \emph{organic} bugs that actually occurred in development and three \emph{notional} bugs (denoted by $*$), which are other code changes that we deemed interesting ways of making the system incorrect. The test found seven of the organic bugs, which are listed first in Table~\ref{tab:testing}. The remaining four bugs (denoted by $\diamond$) were not caught with our default test harness in the 100,000 iterations (a process that required less than 30 minutes). We believe this is because the inputs and schedules that trigger them are too rare in our distribution. To confirm this, we wrote a custom test case for each bug with a specific input that triggers it and were able to quickly reproduce the bugs, as shown. This method is useful for regression testing, but one could not use it during development with no prior knowledge about the bugs.

### 2015-09-22 experience.tex
some updates

\textbf{Specifics of the system}.
MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary \Azure table. This interface is named \texttt{IChainTable}. A virtual table is backed by an \emph{old} and a \emph{new} table, both of which implement \texttt{IChainTable}. A \emph{migrator} job is responsible for moving all data from the old table to the new table in the background. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same old and new tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

@@

\psharp captures and controls all the interleaving in the system, and systematically explores them. To ensure that \texttt{SpecTable} is never observed to be out of sync with the old and new tables, which could lead to false positives, after the \texttt{Tables} machine processes a backend operation, it enters a state that defers further backend operations until MigratingTable has reported whether the backend operation was a linearization point and (if so) the operation on \texttt{SpecTable} has been completed.

>>>>

\textbf{Specifics of the system}.
MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary \Azure table. This interface is named \texttt{IChainTable}. A virtual table is backed by a pair of \emph{old} and \emph{new} \emph{backend} tables, both of which implement \texttt{IChainTable}. A \emph{migrator} job is responsible for moving all data from the old table to the new table in the background. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same backend tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

@@

\psharp captures and controls all the interleaving in the system, and systematically explores them. To ensure that \texttt{SpecTable} is never observed to be out of sync with the backend tables, which could lead to false positives, after the \texttt{Tables} machine processes a backend operation, it enters a state that defers further backend operations until MigratingTable has reported whether the backend operation was a linearization point and (if so) the operation on \texttt{SpecTable} has been completed.
